R Notebook for MSDepression Project

### 2022-09-23 lab_notebook/lab_notebook.Rmd
Add files via upload

>>>>

#### 20220921

[x] replicated!
[x] Updated the stats in my markdown and changed the name to reflect that it is post replication
[x] big changes - correcting the volume multiplication error
[x] Also changed the effect size by volume plot to be scaled logarithmicly
  [x] Now p value of this regression is 0.0187 (Adjusted R2 0.06).
  [x] Elizabeth thinks we can drop the Boot. Ted??
[x] colors for depressed vs nondepressed plots
[x] figure alternatives (move interaction to figure 4, and have fig 5 just brain + scatter)

#### 20220922

[] no cerebellum -> should I find a way to do a flat representation?

Need to install python and pennlinc toolkit

First installed pip (python3 is what i am using)

1. navigate to your git directory of choice (/Users/eballer/BBL/msdepression/erica_local_git/)
2. git clone https://github.com/PennLINC/PennLINC-Kit.git 
3. Activate your python environment of choice [python3]
4. in the cloned directory: pip install -e . (/Users/eballer/BBL/msdepression/erica_local_git/PennLINC-Kit)
5. That should do it.. you can then load up your python interpreter and should be able to import pennlinckit, or from pennlinckit import … where … is whatever function or subpackage you want to import
